Comments on Blair and Sambanis, 2020, \"Forecasting Civil Wars: Theory and Structure in an Age of 'Big Data' and Machine Learning\", *JCR*

### 2020-06-01 paper.Rmd
start revising paper; drop in new tables

---
title: "Comments on Blair and Sambanis, 2020, \"Forecasting Civil Wars: Theory and Structure in an Age of 'Big Data' and Machine Learning\", *JCR*"
author: Richard K. Morgan and Andreas Beger
date: "`r format(Sys.time(), '%d %B %Y')`"
output: 
  pdf_document:
    keep_tex: false
references:
- id: blair2020forecasting
  title: "Forecasting Civil Wars: Theory and Structure in an Age of 'Big Data' and Machine Learning"
  author:
  - family: Blair
    given: Robert A.
  - family: Sambanis
    given: Nicholas
  container-title: Journal of Conflict Resolution
  type: article-journal
  issued:
    year: 2020
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

@@

![Copy of B&S Table 1](figures/bands-table1.png)

@@

```{r, message=FALSE}
table1 <- read_csv("data/table1-redone.csv") %>%
  mutate(specification = factor(specification, levels = c("escalation", "quad", "goldstein", "CAMEO", "avg"))) %>%
  arrange(model, horizon, specification) %>% 
  pivot_longer(-c(model, horizon, specification), names_to = "ROC Smoothed", values_to = "Value") %>% 
  pivot_wider( names_from = "specification", values_from = "Value") %>% 
  mutate(`ROC Smoothed` = ifelse(`ROC Smoothed` == "smoothed", "Yes", "No"), 
         model = "Base Specification") %>% 
  rename(Escalation = escalation, 
         Quad = quad, 
         Goldstein = goldstein, 
         Avg = avg)

table1 %>%
  knitr::kable(digits = 2, booktabs = TRUE, caption = "Comparison of smoothed and not smoothed AUC-ROC values", align = c(rep("l", 2), rep("c", 6))) %>% 
  # column_spec(c(3), bold = TRUE) %>%
  kableExtra::collapse_rows(1:2, row_group_label_position = 'stack')

```

@@

![Copy of B&S Table 2](figures/bands-table2.png)

@@

```{r, message=FALSE}
escalation_only <- read_csv("data/table1-redone.csv") %>%
  filter(specification=="escalation") %>%
  select(-model) %>%
  mutate(horizon = case_when(horizon=="6 month" ~ "6 months", TRUE ~ horizon))

table2 <- read_csv("data/table2-redone.csv") %>%
  bind_rows(escalation_only) %>%
  mutate(
    specification = factor(
      specification, 
      levels = c("escalation", "escalation with PITF", 
                 "escalation with PITF weights", 
                 "escalation with Split PITF", "PITF"),
      labels = c("Escalation\nOnly", "With PITF Predictors", "Weighted by PITF", "PITF Split Population", "PITF Only"))
  ) %>%
  arrange(horizon, specification) %>% 
  pivot_longer(-c(horizon, specification), names_to = "ROC Smoothed") %>% 
  pivot_wider(names_from = "specification") %>% 
  mutate(`ROC Smoothed` = ifelse(`ROC Smoothed` == "smoothed", "Yes", "No")) %>%
  rename(Horizon = horizon)

table2 %>%
  knitr::kable(
    digits = 2, booktabs = TRUE, 
    caption = "Comparison of smoothed and not smoothed AUC-ROC values for B\\&S Table 2", 
    align = c(rep("l", 2), rep("c", 6))
  ) %>% 
  kableExtra::column_spec(c(2, 5, 7), width = "1.5cm") %>%
  kableExtra::column_spec(3, width = "1.8cm") %>%
  kableExtra::column_spec(c(4, 6), width = "2.2cm") %>%
  kableExtra::collapse_rows(1)

```

@@

>>>>

---
title: "Comments on Blair and Sambanis, 2020, \"Forecasting Civil Wars: Theory and Structure in an Age of 'Big Data' and Machine Learning\", *JCR*"
author: Richard K. Morgan and Andreas Beger and Michael D. Ward
date: "`r format(Sys.time(), '%d %B %Y')`"
output: 
  pdf_document:
    keep_tex: false
references:
- id: blair2020forecasting
  title: "Forecasting Civil Wars: Theory and Structure in an Age of 'Big Data' and Machine Learning"
  author:
  - family: Blair
    given: Robert A.
  - family: Sambanis
    given: Nicholas
  container-title: Journal of Conflict Resolution
  type: article-journal
  issued:
    year: 2020
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE)

@@

@@

@@

@@

@@

```{r table1-smooth}
table1_smooth <- read_csv("data/table1-smooth.csv")

table1_smooth %>%
  select(-horizon) %>%
  knitr::kable(
    digits = 2, booktabs = TRUE, 
    caption = "Test set AUC-ROC; replication of the original Table 1 with smoothed ROC curves.") %>% 
  pack_rows(index = c("One-month forecasts" = 9, "Six-month forecasts" = 9))
```

```{r table1-nosmooth}
table1_nosmooth <- read_csv("data/table1-nosmooth.csv")

table1_nosmooth %>%
  select(-horizon) %>%
  knitr::kable(
    digits = 2, booktabs = TRUE, 
    caption = "Test set AUC-ROC; replication of the original Table 1 \\textit{without} smoothed ROC curves.") %>% 
  pack_rows(index = c("One-month forecasts" = 9, "Six-month forecasts" = 9))
```

```{r table2-smooth}
table2_smooth <- read_csv("data/table2-smooth.csv")

table2_smooth %>%
  dplyr::select(-Model) %>%
  rename(Horizon = horizon) %>%
  knitr::kable(
    digits = 2, booktabs = TRUE, 
    caption = "Test set AUC-ROC for Models including PITF; original version based on smoothed ROC curves") 
```

```{r table2-nosmooth}
table2_nosmooth <- read_csv("data/table2-nosmooth.csv")

table2_nosmooth %>%
  dplyr::select(-Model) %>%
  rename(Horizon = horizon) %>%
  knitr::kable(
    digits = 2, booktabs = TRUE, 
    caption = "Test set AUC-ROC for Models including PITF; version \\textit{without} smoothed ROC curves") 
```
